Working Title - Fruit Picker Robot

### 2022-12-19 Exam/example-paper.tex
nah

\hypersetup{%
  pdftitle  = {Working Title - Fruit Picker Robot},
  pdfauthor = {8510},
  pdfsubject = {Introduction to Autonomy},
  pdfkeywords = {Robotics, Automation, Autonomy, Agriculture},
  colorlinks,
  linkcolor=black,
  urlcolor=black,
  citecolor=black,
  pdfpagelayout = SinglePage,
  pdfcreator = pdflatex,
  pdfproducer = pdflatex}

@@

\title{Working Title - Fruit Picker Robot}
\author[1]{8510}
\affil[1]{IMS, Vestfold, Norway, {\small\texttt{anonymous@usn.no}}}
%\affil[2]{Company, Country, {\small\texttt{name3@company}}}

@@

\maketitle\thispagestyle{empty} %% <-- you need this for the first page
\abstract{%
This research paper explores the idea of an autonomous ground vehicle that possesses the ability to harvest fruit, such as strawberries. An introductory, holistic approach is taken, thus social, economic, technical and ... are investigated and discussed.

}

@@

\section{Introduction}
Why?

In the following section, short style guidelines are given.

\subsection{Title and Authors}
Words should be capitalized in the title, e.g., ``This is an Example of
a Correct Title''.  The author information should at least include
name, affiliation (department, university, country). Addresses and
emails are optional but strongly recommended.

\subsection{Abstract and Keywords}

The abstract should be written as one paragraph. It is not recommended
to exceed 150 words.

Appropriate keywords describing the content of the paper should be
supplied as a comma separated list.

\subsection{Fonts}

For all standard body text \emph{Times New Roman} with regular font style, and font size 10.5pt should be used. To emphasize a text or a word, use \emph{italic font style}. For verbatim text embedded in running text, including code fragments, use the style {\code{texttt}} with font Courier New with size 9.5pt should be used (1pt smaller than running text). You can use the provided \code{\textbackslash{}code} macro.

For separate Modelica code examples, use the style font size 9~pt.
Similar for non-Modelica code examples.
For formatting Modelica code this template used the listings definitions from {\small\url{https://github.com/modelica-tools/listings-modelica}} (included in the package).
Code listings are cross-referenced as for example \autoref{lst:while-loop}.

\begin{lstlisting}[caption=A while loop,label=lst:while-loop]
while x<20 loop
  x := x+y*2;
end while;
\end{lstlisting}

\subsection{Lists}

Bullets should be created with the \code{itemize} environment:
\begin{itemize}
\item The first text item.
\item The second text item.
\end{itemize}
Numbered items should be created with the \code{enumerate} environment:
\begin{enumerate}
\item The first text item.
\item The second text item.
\end{enumerate}

\section{Methods}
How?

Figures should be numbered and include a description text. All figures
should be referenced within the body text using the capitalized word
``Figure'' followed by the figure number. For example,
\autoref{fig:figure1} shows a figure located inside one column and
\autoref{fig:figure2} illustrates how a figure can span over two
columns.
You should use vector graphics such as (SVG, EPS, PDF, EMF) rather than raster images such as (JPG, PNG) whenever possible.
Photographs naturally should be raster images.
Rather than using print screen you can often use the "Print" option of software to produce a PDF and especially plots can often be printed or exported to tools that produce vector graphic plots.
If you need to convert vector images between different formats, \textcite{inkscape} is very handy.

\begin{figure}[b]
\centering
\includegraphics[width=0.4 \textwidth]{resources/figure1}
\caption{An example of a figure that fits into one column.}
\label{fig:figure1}
\end{figure}

\begin{figure*}[t]
\centering
\includegraphics[width=0.9 \textwidth]{resources/figure2}
\caption{Another example of a figure that spans over two columns.}
\label{fig:figure2}
\end{figure*}

@@

>>>>

\usepackage[final]{pdfpages}

\hypersetup{%
  pdftitle  = {Fruit-Harvesting Robots: A Multifaceted Technology with Implications for Society, Sustainability, and the Agriculture Industry}, %TODO
  pdfauthor = {8510},
  pdfsubject = {Introduction to Autonomy},
  pdfkeywords = {Robotics, Automation, Autonomy, Agriculture},
  colorlinks,
  linkcolor=black,
  urlcolor=black,
  citecolor=black,
  pdfpagelayout = SinglePage,
  pdfcreator = pdflatex,
  pdfproducer = pdflatex}

@@

\title{Working Title - Fruit Picker Robot} %TODO
\author[1]{8510}
\affil[1]{IMS, Vestfold, Norway, {\small\texttt{223786@usn.no}}}
%\affil[2]{Company, Country, {\small\texttt{name3@company}}}

@@

\maketitle\thispagestyle{empty} %% <-- you need this for the first page
\abstract{%
This research paper examines the social, sustainable, technical, and applied aspects of autonomous fruit-harvesting robots, a technology with the potential to transform the agriculture industry. The study explores the impacts of these robots on labor shortages, the environment, and the agriculture industry, as well as the technical challenges and advances in their development. The applied aspects of autonomous fruit-harvesting robots, including their design and deployment, are also examined.
} %TODO

@@

\section{Introduction}
The development of autonomous fruit-harvesting robots has the potential to revolutionize the way that fruit is grown and harvested, with numerous social, sustainable, technical, and applied implications. As the demand for fresh fruit continues to grow, the use of these robots offers a promising solution to the challenges of labor shortages, increased costs, and environmental impacts in the agriculture industry.

This research paper aims to explore the various aspects of autonomous fruit-harvesting robots, including their social, sustainable, technical, and applied dimensions. By examining the current state of the technology and its potential future developments, we seek to shed light on the ways in which these robots could transform the agriculture industry and the potential impacts they may have on society and the environment.

In the social realm, autonomous fruit-harvesting robots have the potential to address labor shortages and reduce the reliance on human labor in the agriculture sector. They could also have implications for the distribution of wealth and the structure of rural communities, as well as for the safety and health of workers.

Sustainability is also a key concern in the development and use of autonomous fruit-harvesting robots. These robots have the potential to reduce the environmental impacts of fruit production, including greenhouse gas emissions, water use, and soil degradation. They could also contribute to food security and reduce waste by improving the efficiency and accuracy of fruit harvesting.

Technically, the development of autonomous fruit-harvesting robots requires utilization of a wide range of fields, including: robotics, computer vision, machine learning, and sensor technology. These tools are crucial to the success and widespread adoption of the technology.

Finally, the applied aspects of autonomous fruit-harvesting robots are vast and varied, ranging from the design and deployment of the robots themselves to the integration of the technology into existing fruit production systems. The potential benefits and challenges of these applied aspects will be a key focus of this research paper.

Overall, the autonomous fruit-harvesting robot system is a complex and multifaceted technology that holds great promise for the future of agriculture. By examining the various social, sustainable, technical, and applied aspects of this technology, I hope to shed light on its potential impacts and contributions to society and the environment.

\subsection{Social impacts, include distribution of wealth}
\subsection{Value = Sustainability}
\subsection{Existing solutions}
\subsection{Applied aspects (The target environment)}

\subsection{}

\section{Methods}
The goal of this research paper was to explore the social, sustainable, technical, and applied aspects of a fruit-harvesting robot system. To achieve this goal, I used a combination of literature research, brainstorming, and deductive reasoning.

Literature research was the primary method used to gather information for this study. I conducted a comprehensive review of the literature on robotics, including academic articles, textbooks, and news articles.

I searched for sources using relevant keywords and databases, such as Google Scholar, Scopus, and IEEE Xplore. The literature review allowed us to identify the key issues and challenges related to the social, sustainable, technical, and applied aspects of fruit-harvesting robots.

In addition to literature research, I also used brainstorming and deductive reasoning to identify and explore additional questions and issues related to the topic. We held several brainstorming sessions to generate ideas and questions about the social, sustainable, technical, and applied aspects of fruit-harvesting robots. We then used deductive reasoning to narrow down the focus of the study and to develop the research questions and hypotheses.

Overall, the combination of literature research, brainstorming, and deductive reasoning allowed us to comprehensively explore the social, sustainable, technical, and applied aspects of a fruit-harvesting robot system and to identify the key issues and challenges related to this technology.

%TODO this is all trash

@@

\newpage
\onecolumn
\appendix
\section[Section 1]{Assignments for section 1}
\label{paper-w1}
This appendix includes initial definitions of the fruit picker robot including diagrams and cartoons. In addition it features discussions on legal and ethical aspects, as well as a discussion on human-automation interaction issues.
\includepdf[pages=-,openright,width=\textwidth]{resources/W1.pdf}
\section[Section 1]{Assignments for section 2}
\label{paper-w2}
This appendix revolves around motivations or key drivers for the system from multiple perspectives. This discussion includes topics such as cost, labor dependance, product quality, sustainability, and a look at UNs SDGs. It also includes a safety and security discussion followed by a HAZID analysis. Finally a business model canvas is included.
\includepdf[pages=-,openright,width=\textwidth]{resources/W2.pdf}
\section[Section 1]{Assignments for section 3}
\label{paper-w3}
This appendix contains technical information on the organization of software in the system. It includes a system diagram, a layered architecture diagram, a reflection on data collection, and a reflection about learning in the system. 
\includepdf[pages=-,openright,width=\textwidth]{resources/W3.pdf}
\section[Section 1]{Assignments for section 4}
\label{paper-w4}
This final appendix describes capabilities of autonomous systems, different frameworks used for robotics, industrial applications, operational boundaries of systems, and finally an overview of overall capabilities required of the fruit-picker system.
\includepdf[pages=-,openright,width=\textwidth]{resources/W4.pdf}

%\appendix
%\renewcommand{\appendixname}{W1} %% So we get 'Paper X' displayed instead
%
%
%\chapter[Section 1]{Assignments for section 1}
%\label{paper-w1}
%
%
%\includepdf[pages=-,openright,width=\textwidth]{resources/W1.pdf}

%
%You can omit the \texttt{.pdf} when specifying the \texttt{Filename}. Also you should include always include the option \texttt{openright} since it would look strange to have the paper starting at the back of the cover page.
%
%There are more options like only adding specific pages:
%\begin{verbatim}
%\includepdf{pages=2-6,openright}{Filename.pdf}
%\end{verbatim}

%For more options see Appendix~\ref{paper-b} where the most important pages of the \texttt{pdfpages} manual were inlcuded using \texttt{pdfpages}.

%%% Command to include a PDF file directly including all pages:

%\chapter[Short Title of Paper B]{Title of Paper B}
%\label{paper-b}
%Short descriptive text of paper follows here.
%
%Here we included the first five pages of the \texttt{pdfpages} manual itself.
%
%\includepdf[pages=1-5,openright]{fig/pdfpages}
%
